A thesis draft

### 2018-09-21 draft.tex
Add new content, new section about MANO

Starting with the first step of creating a MANO able to process incoming data
packets through VNF functions, we encountered that many networking tools
already present in the market required some tweaking and some integrations,
shifting our goal to create a complete  European Telecommunications Standards
Institutes (ETSI) Management and orchestrator (MANO) testbed instead, following
the specifications suggested in the RFC 7665, thus implementing only the first
three requisites, without digging in the satellite data flow optimization.
\todo{This section needs to be expanded a lot!!!}

>>>>

Starting with the first step of creating a MANO able to process incoming data
packets through VNF functions, we encountered that many networking tools
already present in the market required some tweaking and some integrations,
shifting our goal to create a complete  European Telecommunications Standards
Institutes (ETSI) Management and orchestrator (MANO) testbed instead, following
the specifications suggested in the RFC 7665, thus implementing only the first
three requisites, without digging in the satellite data flow optimization. In 
particular, we discovered how, these tools, were suitable to create ETSI MANO 
and VNFs using virtual machine or exploiting cloud tecnhologies, while they 
were not designed with enough flexibility to be able to accept new 
virtualization technologies such as Docker. In the next session we are going to 
take a deep analysis of the cited technologies, in order to provide to the 
reader enough context to be able to understand our design choices we are going 
to describe later.

\section{MANO}

\todo{This section needs to be expanded a lot!!! In particular, we should put 
some focus about VNF and MANO, introducing them}

\noindent With this in mind, we performed a requirements analysis described in 
the next chapter.\todo{This should be put at the end of the introduction.}
